Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-06 talk/dls2012/paper.tex
clarify
improve transition

\reva{
I think the motivation section is great, in particular for readers
who are less familiar with compiler/JIT optimizations. However,
section 4 starts with "yet another example" - at least this was my
impression when reading it. I understand the differences and
everything, but still, you might consider to improve the transition
between sections 3 and 4.
}

For the purpose of this paper, we are going to use a tiny interpreter for a dynamic language with
 a very small object
model, that just supports an integer and a float type (this example has been taken from a previous paper \cite{bolz_allocation_2011}). The objects support only
one operation, \lstinline{add}, which adds two objects (promoting ints to floats in a
mixed addition). The implementation of \lstinline{add} uses classical Smalltalk-like
double-dispatching.
%These classes could be part of the implementation of a very
%simple interpreter written in RPython.
The classes can be seen in
Figure~\ref{fig:objmodel} (written in RPython).

@@

Other interesting interpreters that are helped greatly by this optimization are
for example our Prolog interpreter written in RPython
\cite{carl_friedrich_bolz_towards_2010}. Prolog programs often contain tight
loops that perform list processing. Furthermore we experimented with a language
for writing numerical kernel used for array manipulation. The exact extent is
out of scope for this paper.

>>>>

The last section gave a motivating but unrealistically small example.
This section will define a slightly larger example that the rest of the paper
uses to demonstrate the effect of optimizations.
For this we are going to use a tiny interpreter for a dynamic language with
 a very small object
model, that just supports an integer and a float type (this example has been taken from a previous paper \cite{bolz_allocation_2011}). The objects support only
one operation, \lstinline{add}, which adds two objects (promoting ints to floats in a
mixed addition). The implementation of \lstinline{add} uses classical
double-dispatching.
%These classes could be part of the implementation of a very
%simple interpreter written in RPython.
The classes can be seen in
Figure~\ref{fig:objmodel} (written in RPython).

@@

Other interesting interpreters that are helped greatly by this optimization are
for example our Prolog interpreter written in RPython
\cite{carl_friedrich_bolz_towards_2010}. Prolog programs often contain tight
loops that perform list processing. Furthermore we experimented with a Python library
for writing numerical kernels doing array manipulation. The exact extent is
out of scope for this paper.
